\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-08 doc/sui14/interaction.tex
Fix grammar issues pointed out by SUI R2

IR signals are used for initial line-of-sight targeting; subsequently, we use bi-directions wireless communication to send information such as target IDs and signal strength from targets to back to Glass. We have chosen the commercial off-the-shelf ZigBee implementation (XBee based on 802.15.4 radio) for this purpose (see Figure~\ref{fig:architecture}). This architecture was mostly chosen for reasons of expediency and we do not claim optimality for prototyping decisions. Future head-mounted devices could clearly integrate IR emitters; other wireless techniques (WiFi, Bluetooth) can also be used.

@@

{\bf Scan:} The user first scans the environment to locate the position of the target. During this stage, Glass constantly sends out IR signals, and  targets offer immediate visual feedback when they receive a signal. The user confirms his desire to connect to a target by tapping on the Glass touchpad. Glass collects the responses from targets that have received IR reception through the backchannel of XBee. If there is only one single target in IR range, it is automatically selected. However, in a dense environment where multiple targets are within range, the user needs refine his selection.

>>>>

IR signals are used for initial line-of-sight targeting; subsequently, we use bidirectional wireless communication to send information such as target IDs and signal strength from targets back to Glass. We have chosen the commercial off-the-shelf ZigBee implementation (XBee based on 802.15.4 radio) for this purpose (see Figure~\ref{fig:architecture}). This architecture was mostly chosen for reasons of expediency and we do not claim optimality for prototyping decisions. Future head-mounted devices could clearly integrate IR emitters; other wireless techniques (WiFi, Bluetooth) can also be used.

@@

{\bf Scan:} The user first scans the environment to locate the position of the target. During this stage, Glass constantly sends out IR signals, and  targets offer immediate visual feedback when they receive a signal. The user confirms his desire to connect to a target by tapping on the Glass touchpad. Glass collects the responses from targets that have received IR reception through the backchannel of XBee. If there is only one single target in IR range, it is automatically selected. However, in a dense environment where multiple targets are within range, the user needs to refine his selection.

### 2014-08-08 doc/sui14/iteration1.tex
Fix grammar issues pointed out by SUI R2

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. Afterward, participants were asked to complete a survey of primarily open-ended answers about their experience.

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and pleasurable. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen}. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.

>>>>

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. Afterward, participants were asked to complete a survey of primarily open-ended questions about their experience.

@@

As for the qualitative feedback, 11 out of 14 participants preferred IR selection over list mode (two preferred list, one was undecided). While both interfaces were judged similarly on overall ease of connecting, IR selection was perceived to be more direct and pleasant. One user noted benefit of {\em IR selection}  \studyquote{allowing users to focus on the targeted objects instead of the screen}. \achal{This seems rather weak... Don't really need all the quotes.} One subject called it \studyquote{natural to interact with things just by looking at them}. Another mentioned that \studyquote{it's really convenient that what I'm looking at is what I'm targeting}.

### 2014-08-08 doc/sui14/relatedwork.tex
Fix grammar issues pointed out by SUI R2

\subsection{Pointing in Physical Spaces}
Rukzio ~\cite{rukzio_experimental_2006} studied alternative methods for selecting devices in physical spaces and found that users strongly preferred either tapping target appliances with a mobile device or pointing at a distance to browsing a list. Several other approaches to spatial selection with handheld devices~\cite{beigl_point_1999,patel_2-way_2003,wilson_xwand:_2003,schmidt_picontrol:_2012,kemp_point-and-click_2008} or finger-worn devices~\cite{merrill_augmenting_2007} exist. 
%and exchanging information with smart infrastructure sensor networks ~\cite{lifton_tricorder:_2007,mittal_ubicorder:_2011,costanza_sensortune:_2010}. 
In some techniques, users select objects of interest with laser pointers; however, the laser dot's small target area makes it poorly matched to head orientation input.
Other approaches rely on virtual room models in which a user's location is estimated using IMU-based orientation sensing~\cite{wilson_xwand:_2003,lifton_tricorder:_2007} -- in contrast, our technique does not require a static map ahead of time.
%Other targeting systems use IR with handheld pointers~\cite{swindells_that_2002} as well as wearable devices such as rings and Bluetooth audio earpieces~\cite{merrill_augmenting_2007} to connect to smart devices. 
Our system tackles an unresolved issue of prior approaches -- navigating an area dense with potential targets and resolving selection ambiguity.

>>>>

\subsection{Pointing in Physical Spaces}
Rukzio et al. ~\cite{rukzio_experimental_2006} studied alternative methods for selecting devices in physical spaces and found that users strongly preferred either tapping target appliances with a mobile device or pointing at a distance to browsing a list. Several other approaches to spatial selection with handheld devices~\cite{beigl_point_1999,patel_2-way_2003,wilson_xwand:_2003,schmidt_picontrol:_2012,kemp_point-and-click_2008} or finger-worn devices~\cite{merrill_augmenting_2007} exist. 
%and exchanging information with smart infrastructure sensor networks ~\cite{lifton_tricorder:_2007,mittal_ubicorder:_2011,costanza_sensortune:_2010}. 
In some techniques, users select objects of interest with laser pointers; however, the laser dot's small target area makes it poorly matched to head orientation input.
Other approaches rely on virtual room models in which a user's location is estimated using IMU-based orientation sensing~\cite{wilson_xwand:_2003,lifton_tricorder:_2007} -- in contrast, our technique does not require a static map ahead of time.
%Other targeting systems use IR with handheld pointers~\cite{swindells_that_2002} as well as wearable devices such as rings and Bluetooth audio earpieces~\cite{merrill_augmenting_2007} to connect to smart devices. 
Our system tackles an unresolved issue of prior approaches -- navigating an area dense with potential targets and resolving selection ambiguity.
